MSDS6306_CaseStudy_2

### 2017-12-04 Presentation/MSDS6306_CaseStudy_2.Rmd
Updating RMD file. Pushing the Column Name translation information to GitHub.

# Load Libraries
```{r}
library(repmis)
library(dplyr)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(sqldf)
library(kimisc)
library(XML)
library(RCurl)
library(rvest)
library(plyr)
library(pastecs)
```

# R - environment
```{r}
sessionInfo()
```

# Set Base Directory:

@@

# Set Other Working Directories and File Path
```{r}
DataDir <- paste(BaseDir,"Data", sep = "/")
CodeDir <- paste(BaseDir,"Code", sep = "/")
PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")

@@

# Read the Data File
```{r}
ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")

dim(ProcrastinationData)
```

@@

>>>>

## Load Required R Libraries
```{r}
library(repmis)
library(dplyr)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(sqldf)
library(kimisc)
library(XML)
library(RCurl)
library(rvest)
library(plyr)
library(pastecs)
```

## R - environment List of libraries used by the session
```{r}
sessionInfo()
```

## Set Base Directory:

@@

## Set Other Working Directories and File Path
```{r}
DataDir <- paste(BaseDir,"Data", sep = "/")
CodeDir <- paste(BaseDir,"Code", sep = "/")
PresenatationDir <- paste(BaseDir,"Presentation", sep = "/")

@@

## Read the Data File
```{r}
ProcrastinationData <- read.csv(ProcrastinationDataFile, sep = ",", header = T, na.strings = "")
```

@@

#### The data file has been read and stored in a temporary data frame (ProcrastinationData). The column names have been standardized to be 12 characters long or lesser.

```{r}
dim(ProcrastinationData)
```
